% ============================================================
%  Section: Introduction & Project Scope
% ============================================================

The New York City subway system is one of the largest and most complex urban
transit networks in the world, serving millions of riders daily across
\textbf{472 stations} and \textbf{27 lines}. Understanding ridership patterns,
identifying peak usage periods, and tracking station-level traffic are problems
with real operational significance for the MTA and for city planners.

This project, \textit{MTA Transit Pulse}, builds a complete data management pipeline
around the MTA's publicly available weekly turnstile data. Rather than simply
downloading and plotting a spreadsheet, the goal is to design and implement a
\textit{system}: one that collects, validates, stores, queries, and presents data
in a reproducible and maintainable way.

\subsection{Motivation}

% Write 2-3 sentences about why this project is interesting to you personally
% and why subway data is a meaningful dataset to work with.
\textit{[Add your personal motivation here.]}

\subsection{Project Objectives}

The system is designed to satisfy the following objectives:

\begin{enumerate}
    \item Automate the collection of MTA turnstile CSV data from the public portal.
    \item Clean and validate raw data, handling known MTA data quality issues.
    \item Store the processed data in a normalized SQLite relational database.
    \item Enable SQL-driven analysis of ridership patterns by line, station, and time.
    \item Provide automated database backups and version-controlled source code.
    \item Deliver an interactive Streamlit dashboard for non-technical data exploration.
    \item Document the full pipeline in a reproducible GitHub repository.
\end{enumerate}

\subsection{Scope and Limitations}

The project focuses on \textbf{entry and exit counts} from MTA turnstiles, which serve
as a proxy for ridership. The initial dataset covers
\textit{[insert your date range once you decide it]}.
Real-time train positions and delay data are outside the scope of this version,
though the database schema is designed to accommodate future enrichment.
